### 2013-10-03 src2/thesis.tex
apa
update

%stuff
\usepackage{latexsym}
\usepackage{tikz,pgflibraryshapes}
\usepackage{booktabs}
%%

@@

\newcommand{\thesistitle}{Not decided upon}
\newcommand{\dept}{Department of Computer Science and Engineering}
\newcommand{\uni}{Chalmers University of Technology and G\"oteborg University}
\newcommand{\group}{Functional Programming Research Group}

\begin{document}

@@

\noindent\copyright {\sc {Bo Joel Svensson}}, 2013 \\*[5mm]
\vspace{1cm}

\noindent Technical Report ..D\\
\noindent ISSN                \\
\noindent \dept \\
\noindent \group\\

@@

\section*{Acknowledgements}

@@

@@

@@

\chapter{GPU programming papers}

@@

\section{Obsidian: A Domain Specific Embedded Language for Parallel Programming of Graphics Processors}
%\addcontentsline{toc}{chapter}{Obsidian: A Domain Specific Embedded Language for
%Parallel Programming of Graphics Processors}

@@

\section{Obsidian: GPU Computing Using Haskell}
%\addcontentsline{toc}{chapter}{Obsidian: GPU Computing Using Haskell}

@@

\section{Expressive Array Constructs in an Embedded GPU Kernel Programming Language}
%\addcontentsline{toc}{chapter}{Expressive Array Constructs in an Embedded GPU Kernel Programming Language}

@@

\section{Counting and Occurrence Sort for GPUs using an Embedded Language}
%\addcontentsline{toc}{chapter}{Counting and Occurrence Sort for GPUs using an Embedded Language}

@@

\section{Simple and Compositional Reification of Monadic Embedded Languages}
%\addcontentsline{toc}{chapter}{Simple and Compositional Reification of Monadic Embedded Languages}

@@

\chapter{Retargetable parallel programming papers}
% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\section{Programming Future Parallel Architectures with Haskell and Intel ArBB}
%\addcontentsline{toc}{chapter}{Parallel Programming in Haskell Almost for Free}

@@

\section{Parallel Programming in Haskell Almost for Free}
%\addcontentsline{toc}{chapter}{Parallel Programming in Haskell Almost for Free}

>>>>

%stuff
\usepackage{latexsym}
\usepackage{tikz,pgflibraryshapes}
\usetikzlibrary{shapes,snakes,positioning}
\usepackage{pgfplots}
\usepackage{booktabs}
%%

@@

\newcommand{\thesistitle}{Embedded Languages for Data Parallel Computation}
\newcommand{\dept}{Department of Computer Science and Engineering}
\newcommand{\uni}{Chalmers University of Technology and G\"oteborg University}
\newcommand{\group}{Functional Programming Research Group}

% ---------------------------------------------------------------------------
% Papers 
% ---------------------------------------------------------------------------
\newcommand{\paperBB}{Simple and Compositional Reification of Monadic Embedded Languages}
\newcommand{\paperIFL}{Obsidian: A Domain Specific Embedded Language for Parallel Programming of Graphics Processors}
\newcommand{\paperPAPP}{GPGPU Kernel Implementation and Refinement using Obsidian} 
\newcommand{\paperEXPRESSIVE}{Expressive Array Constructs in an Embedded GPU Kernel Programming Language}
\newcommand{\paperCSORT}{Counting and Occurrence Sort for GPUs using an Embedded Language}
\newcommand{\paperHL}{A High-Level Embedded Language for Low-Level GPU Kernel Programming}
\newcommand{\paperARBB}{Programming Future Parallel Architectures with Haskell and Intel ArBB}
\newcommand{\paperEMBARBB}{Parallel Programming in Haskell Almost for Free}

% ---------------------------------------------------------------------------
% BEGIN ! 
% ---------------------------------------------------------------------------
\begin{document}

@@

\noindent\copyright {\sc {Bo Joel Svensson}}, 2013 \\ 
\vspace{1cm}

\noindent Technical Report 101D\\
\noindent ISSN                 \\
\noindent \dept \\
\noindent \group\\

@@

\section*{Acknowledgments}

@@

\cleardoublepage
\clearpage

@@

\chapter{About this thesis}

This thesis contains an introduction and a selection of papers. The introduction 
gives background and context to the papers.

\section{Papers}

The papers contained in this thesis falls in three different categories. 
\begin{itemize} 
\item General EDSL methodology in chapter~\ref{chap:EDSLImplementation}. 
\item GPU Programming using an EDSL in chapter~\ref{chap:GPUProgramming}. 
\item Retargetable parallel programming in chapter~\ref{chap:ArBB}. 
\end{itemize}

\subsection{EDSL implementation papers}

\subsubsection{\paperBB}

apa apa apa bepa cepa apa

\subsection{GPU Programming papers}

\subsubsection{\paperIFL}

\subsubsection{\paperPAPP}

\subsubsection{\paperEXPRESSIVE}

\subsubsection{\paperCSORT}

\subsubsection{\paperHL}

\subsubsection{Retargetable parallel programming}

\subsubsection{\paperARBB}

\subsubsection{\paperEMBARBB}

@@

\chapter{EDSL implementation papers}
\label{chap:EDSLImplementation}
% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\section{\paperBB}
\label{sec:paperBB}
%\addcontentsline{toc}{chapter}{Simple and Compositional Reification of Monadic Embedded Languages}

\chapter{GPU programming papers}
\label{chap:GPUProgramming}

@@

\section{\paperIFL}
\label{sec:paperIFL}
%\addcontentsline{toc}{chapter}{Obsidian: A Domain Specific Embedded Language for
%Parallel Programming of Graphics Processors}

@@

\section{\paperPAPP}
\label{sec:paperPAPP}
%\addcontentsline{toc}{chapter}{Obsidian: GPU Computing Using Haskell}

@@

\section{\paperEXPRESSIVE}
\label{sec:paperEXPRESSIVE}
%\addcontentsline{toc}{chapter}{Expressive Array Constructs in an Embedded GPU Kernel Programming Language}

@@

\section{\paperCSORT}
\label{sec:paperCSORT}
%\addcontentsline{toc}{chapter}{Counting and Occurrence Sort for GPUs using an Embedded Language}

@@

\section{\paperHL}
\label{sec:paperHL}
%\addcontentsline{toc}{chapter}{Simple and Compositional Reification of Monadic Embedded Languages}

\input{./hl/paperThesis}

@@

\chapter{Retargetable parallel programming papers}
\label{chap:ArBB}
% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\section{\paperARBB}
\label{sec:paperARBB}
%\addcontentsline{toc}{chapter}{Parallel Programming in Haskell Almost for Free}

@@

\section{\paperEMBARBB}
\label{sec:paperEMBARBB}
%\addcontentsline{toc}{chapter}{Parallel Programming in Haskell Almost for Free}
